Supplementary Information: \\ Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-12-22 SI.tex
modify the SI file

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
\usepackage{times}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage{braket}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

\usepackage{xr-hyper} 
%\usepackage{xr}
\externaldocument[main-]{paper}

@@

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}

@@

\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
\begin{document}

@@

\subsection{Profile of induced dipoles of 2D material}
\label{sec:dipole-plot}
Here we show in detail the
$\Delta {\rho}=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
the 2H-MoS$_{2}$ slab in main text Figure \ref{main-fig-1}. The
density $\Delta \rho$ is calculated via $\Delta \rho(z) = \frac{1}{S} \int_{S} \Delta \rho (x,y;z) dx dy $, 
where $S$ is the surface of the unit cell perpendicular to the given direction, in this case $z$. 
%
As can be seen in Figure \ref{fig:rho-profile} the induced charges on
the MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}
centered at the middle of the layer. This corresponds to about 5-6 \AA
from each side.  When the SL size $L \gg$12 \AA{} as in the first
principle calculations done in the main text, the induced dipoles from
the periodic images do not interact, and thus give the converged
values of $\alpha_{\mathrm{2D}}$.

@@

Here we will show the results of dielectric properties calculated
using many-body Green function method (G$_{0}$W$_{0}$) and with
electron-hole interactions at the level of the Bethe-Salpeter equation
(G$_{0}$W$_{0}$–BSE). Frequency-dependent dielectric functions,
$\varepsilon_{\mathrm{SL}}(L)$, were calculated at the level of
G$_{0}$W$_{0}$ and G$_{0}$W$_{0}$+BSE levels using VASP. For the
calculations on G$_{0}$W$_{0}$, a 12$\times$12$\times$1 $\Gamma$-centered k-grid was
used along with an 800 eV energy cutoff in the plane waves and in
calculation of the response function. 120 bands (4 occupied and 116
unoccupied) were used in the calculation of
$\varepsilon_{\mathrm{SL}}(\omega)$ of monolayer BN, with local-field
effects being included on the RPA level. For the calculation of the
Bethe-Salpeter equation, the Tamm-Dancoff approximation was used with
two occupied and two unoccupied bands being included in the
calculation.

@@

We first compare the case of a monolayer of BN within a varying
superlattice $L$ calculated using PBE and G$_{0}$W$_{0}$ as shown in
Figure \ref{fig:GW-PBE-alpha}.  Both
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ do not converge as a function of
$L$ despite of the separation utilized in the simulations (Figure
\ref{fig:GW-PBE-alpha}{\bf a}-{\bf c}). However, corresponding 2D
polarizabilities are almost $L$-independent (Figure
\ref{fig:GW-PBE-alpha}{\bf b}-{\bf d}). It is worth noting that since
the G$_{0}$W$_{0}$ method has better estimation of the bandgap,
$\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller
using G$_{0}$W$_{0}$ than in PBE functionals.
\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
 \caption{{\bf Variation of 
   $\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for
   monolayer BN calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.}
   \textbf{a}-{\bf b}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\parallel}$ as function of $L$, respectively.    
  \textbf{c}-{\bf d}. $\varepsilon_{\mathrm{SL}}^{\perp}$ and 
  $\alpha_{\mathrm{2D}}^{\perp}$ as
   function of $L$. 
   In all cases the values obtained using
   G$_{0}$W$_{0}$ method is smaller than that using PBE method due to
   better estimation of the bandgap.}
  \label{fig:GW-PBE-alpha}
\end{figure}

Next we will investigate the frequency-dependent dielectric properties of the 2D materials using various methods. The imaginary part of the frequency-dependent dielectric function of an periodic system is calculated using the following relation:

@@

\begin{equation}
  \varepsilon_{\alpha\beta}^{(1)}(\omega)=1+\frac{2}{\pi}\int_0^\infty\frac{\varepsilon_{\alpha\beta}^{(2)}(\omega')\omega'}{\omega'^2-\omega^2}d\omega'
\end{equation}

We calculate the frequency-dependent dielectric properties of BN with
varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$--BSE. 
Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out} show the
magnitudes of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
$\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
throughout the whole frequency range at PBE level. The $L$-dependency can also be
removed using main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, yielding lattice-independent
polarizabilities throughout the frequency domain (Figure \ref{fig:PBE-omega-in}{\bf b}-{\bf d} and \ref{fig:PBE-omega-out}{\bf b}-{\bf d}). 
%
Note that when extracting the frequency-dependent 2D polarizabilities
from main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, the peak position in energy
$\hbar \omega$ from $\varepsilon_{\mathrm{SL}}$ is preserved. This is
explained by the fact that the local extrema from spectra of
$\varepsilon_{\mathrm{SL}}$ is also the local extrema in corresponding
$\alpha_{\mathrm{2D}}$, since when
$\partial \varepsilon_{\mathrm{SL}}(\omega) / \partial \omega = 0 $,
we have
\begin{subequations}
\begin{eqnarray}
  \label{eq:extrema-para}
  \frac{\partial \alpha_{\mathrm{2D}}^{\parallel}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0   \\
  \label{eq:extrema-perp}
  \frac{\partial \alpha_{\mathrm{2D}}^{\perp}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{2}}\frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0
\end{eqnarray}
\end{subequations}
which indicates that no corrections in energy are present 
when transforming
$\varepsilon_{\mathrm{SL}}(\omega)$ to $\alpha_{\mathrm{2D}}(\omega)$.
Performing the simulations at the level of G$_{0}$W$_{0}$
we observe blue shifts in energy in $\varepsilon_{\mathrm{SL}}(\omega)$ 
with increasing $L$. Figures \ref{fig:GW-omega-in} and
\ref{fig:GW-omega-out} show that not only the magnitude of the dielectric
functions change with $L$ but also the peak positions. As a result
the obtained polarizabilities also show $L$-dependent peak 
shift (Figures \ref{fig:GW-omega-in} {\bf b}-{\bf d} and
\ref{fig:GW-omega-out}{\bf b}-{\bf d}). This
can be explained by the long-range nature of Coulomb interactions into the self-energy 
$\Sigma=iGW$.

@@

For bulk systems, the accuracy of optical properties calculated
generally ranks by PBE $<$ G\textsubscript{0}W\textsubscript{0} $<$
BSE. This is because the calculation of the frequency-dependent
optical properties of a material involves a summation over the valence
and conduction states. Thus, the accuracy of these states determines
the calculated optical properties. Within Kohn-Sham density functional
theory (KS-DFT), the many-body effects are given by the
exchange-correlation energy which is approximated by functionals based
on the homogenous electron gas. This generally leads to an
underestimation of the bandgap and results in the first optical peak
being lower in energy in comparison to experiment. To go beyond
KS-DFT, the G\textsubscript{0}W\textsubscript{0} approximation
replaces the exchange-correlation energy with the self-energy in a bid
to include many-body effects through the interacting Green's function,
$G$, and the screened Coulomb potential, $W$. This generally leads to
an overestimation of the first optical peak as electron-hole coupling
is not taken into account. This can be remedied by solving the
Bethe-Salpeter equation using the eigenvalues obtained from
G\textsubscript{0}W\textsubscript{0}
(G\textsubscript{0}W\textsubscript{0} + BSE) which generally gives
good agreement with experiment.

Due to the volume dependence of $\Sigma$ in equations \ref{self} and
\ref{quasi}, increasing the vacuum spacing leads to a change in the
calculated quasi-particle eigenergies. This, along with the volume
dependence in the calculation of the dielectric function, leads to an
increase in energy of the peak position and a decrease in its
magnitude with increasing vacuum spacing. Such effect is also
discussed in several other studies
\cite{Rozzi_2006,Hueser_2013_2Dvs3D}, when full Coulomb interaction is
used in a supercell. Including excitonic effects on top of a
G$_0$W$_0$ calculation through solving the Bethe--Salpeter equation
corrects for this energy shift by localizing the exciton within the
slab (Figures \ref{fig:BSE-omega-in} and
\ref{fig:BSE-omega-out}). However, the decrease in the magnitude of
the dielectric function on both components of
$\varepsilon_{\mathrm{SL}}(\omega)$ with increasing vacuum spacing is
still observed.  Using main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def} we can remove the dependence on $L$ as
plotted in Figures \ref{fig:BSE-omega-in}{\bf b}-{\bf d} and
\ref{fig:BSE-omega-out}{\bf b}-{\bf d} with fewer variations on
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$.

@@

Combining the accuray of bandgap estimation, reproducible results of
frequency-dependent dielectric properties and calculation efforts, the
choice of HSE06 hybrid functional seems used in the main text provides
best tradeoff between all aspects.

@@

The major issue when using such rescale
relations comes from the determination of $\delta_{\mathrm{2D}}^{*}$. To
eliminate the modeling error caused by the \textit{a priori} parameter
selection of $\delta$, we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
and use least-square fitting to extract both
$\varepsilon$ and $\delta$, as shown in
Figure \ref{fig:rescale-prb}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.85\linewidth]{img/SI-rescale-PRB.pdf}
  \caption{ Calculated (blue dots) and fitted
    (orange broken lines) $\varepsilon_{\mathrm{SL}}$ as function of
    $L$ for the group 6 TMDCs:
    \textbf{a}. MoS$_{2}$. \textbf{b}. MoSe$_{2}$. \textbf{c}.
    MoTe$_{2}$. \textbf{d}. WS$_{2}$. \textbf{e}. WSe$_{2}$. \textbf{f}.
    WTe$_{2}$. The extracted values of $\varepsilon_{\mathrm{2D}}$ and
    $\delta$ are shown in each subfigure.}
  \label{fig:rescale-prb}
\end{figure}

As can be seen from the fitted results in Figure
\ref{fig:rescale-prb}, the values of $\delta_{\mathrm{2D}}^{*}$ extracted
from both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ are close when $L> 15$
{\AA}. Notably, the $\delta_{\mathrm{2D}}^{*}$ values are generally 10\%
smaller than the interlayer distance in corresponding bulk materials
$L_{\mathrm{bulk}}$ , as shown in Table \ref{tab:delta-L-DFt}. On the
other hand, the extracted $\delta_{\mathrm{2D}}^{*}$ values are closer to
the covalent thickness $\delta_{cov}$ as
described in the main text, with a difference generally smaller than
5\%. Our results indicate that the conventional estimation of the 2D
layer thickness by its bulk interlayer distance
\cite{Matthes_2016,Laturia_2018}, will always lead to
overestimation. On the contrary, the out-of-plane polarizability
$\alpha_{\mathrm{2D}}^{\perp}$ correctly captures the thickness nature
of 2D materials.

@@

One main drawback of the EDM approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{eq:MG-effect-1} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}

@@

which indicate that the characteristic length
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
than $\delta_{\mathrm{2D}}^{*}$ estimated by the effective medium theory,
if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}^{*}$ and
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
$\delta_{\mathrm{2D}}^{*}$ chosen may lead to divergence of
$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
\ref{fig:eps-alpha-error}. Therefore cautions must to taken when
treating the dielectric response of the 2D material using effective
medium theory. In comparison, the 2D polarizability does not require
the guess of the thickness, and therefore is the true descriptor of
the 2D dielectric nature.

>>>>

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,email=true,hyperref=true,keywords=false]{achemso}
%manuscript=suppinfo 
\usepackage{times}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage{braket}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

%\usepackage{xr}
\usepackage{xr-hyper} 
\externaldocument[main-]{paper_v120719}

@@

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Victoria, VIC 3216, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}

@@

\title{Supplementary Information: \\ 
Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
\begin{document}

@@

\subsection{Profile of induced dipoles of 2D material}
\label{sec:dipole-plot}
Here we show in detail the
$\Delta {\rho}=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
the 2H-MoS$_{2}$ slab in main text Figure \ref{main-fig-1}. The
density $\Delta \rho$ is calculated via $\Delta \rho(z) = \frac{1}{S} \int_{S} \Delta \rho (x,y;z) dx dy $, 
where $S$ is the surface of the unit cell perpendicular to a given direction, in this case $z$. 
%
As can be seen in Figure \ref{fig:rho-profile} the induced charges on
the MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}
centered at the middle of the layer. This corresponds to about 5-6 \AA~
from each side.  When the SL size $L \gg$12 \AA{} as in the first
principle calculations shown in the main text, the induced dipoles from
the periodic images do not interact thus giving the converged
values of $\alpha_{\mathrm{2D}}$.

@@

Here we will show the results of dielectric properties calculated
using many-body Green function method (G$_{0}$W$_{0}$) and with
electron-hole interactions at the level of the Bethe-Salpeter equation
(G$_{0}$W$_{0}$-BSE). Frequency-dependent dielectric functions,
$\varepsilon_{\mathrm{SL}}(\omega)$, were calculated at the level of
G$_{0}$W$_{0}$ and G$_{0}$W$_{0}$+BSE levels using VASP. For the
calculations on G$_{0}$W$_{0}$, a 12$\times$12$\times$1 $\Gamma$-centered k-grid was
used along with a 800 eV energy cutoff in the plane waves and in
calculation of the response function. 120 bands (4 occupied and 116
unoccupied) were used in the calculation of
$\varepsilon_{\mathrm{SL}}(\omega)$ of monolayer BN, with local-field
effects being included. For the calculation of the
Bethe-Salpeter equation, the Tamm-Dancoff approximation was used with
two occupied and two unoccupied bands being included.

@@

We first compare the case of a monolayer of BN within a varying
superlattice $L$ calculated using PBE and G$_{0}$W$_{0}$ as shown in
Figure \ref{fig:GW-PBE-alpha}.  Both
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ do not converge as a function of
$L$ despite of the separation utilized in the simulations (Figure
\ref{fig:GW-PBE-alpha}{\bf a}-{\bf c}). However, corresponding 2D
polarizabilities are almost $L$-independent (Figure
\ref{fig:GW-PBE-alpha}{\bf b}-{\bf d}). It is worth noting that since
the G$_{0}$W$_{0}$ method has better estimation of the electronic bandgap,
$\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller
using G$_{0}$W$_{0}$ than in PBE functionals.
%%%
\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
 \caption{{\bf Variation of 
   $\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for
   monolayer BN calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.}
   \textbf{a}-{\bf b}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\parallel}$ as function of $L$, respectively.    
  \textbf{c}-{\bf d}. $\varepsilon_{\mathrm{SL}}^{\perp}$ and 
  $\alpha_{\mathrm{2D}}^{\perp}$ as
   function of $L$. 
   In all cases the values obtained using
   G$_{0}$W$_{0}$ method is smaller than that using PBE method due to
   better estimation of the bandgap.}
  \label{fig:GW-PBE-alpha}
\end{figure}

Next we will investigate the frequency-dependent dielectric properties of the 2D materials using various methods. The imaginary part of the frequency-dependent dielectric function of a periodic system is calculated using the following relation:

@@

\begin{equation}
\label{eq:dft-dielectric-real}
  \varepsilon_{\alpha\beta}^{(1)}(\omega)=1+\frac{2}{\pi}\int_0^\infty\frac{\varepsilon_{\alpha\beta}^{(2)}(\omega')\omega'}{\omega'^2-\omega^2}d\omega'
\end{equation}

We calculate the frequency-dependent dielectric properties of BN with
varying superlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$--BSE. 
Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out} show that the
magnitudes of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
$\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
throughout the whole frequency range at PBE level. The $L$-dependency can also be
removed using main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, yielding lattice-independent
polarizabilities throughout the frequency domain (Figure \ref{fig:PBE-omega-in}{\bf b}-{\bf d} and \ref{fig:PBE-omega-out}{\bf b}-{\bf d}). 
%
Note that when extracting the frequency-dependent 2D polarizabilities
from Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, the peak position in energy
$\hbar \omega$ from $\varepsilon_{\mathrm{SL}}$ is preserved. This is
explained by the fact that the local extrema from spectra of
$\varepsilon_{\mathrm{SL}}$ is also the local extrema in corresponding
$\alpha_{\mathrm{2D}}$, since when
$\partial \varepsilon_{\mathrm{SL}}(\omega) / \partial \omega = 0 $,
we have
\begin{subequations}
\begin{eqnarray}
  \label{eq:extrema-para}
  \frac{\partial \alpha_{\mathrm{2D}}^{\parallel}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0   \\
  \label{eq:extrema-perp}
  \frac{\partial \alpha_{\mathrm{2D}}^{\perp}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{2}}\frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0
\end{eqnarray}
\end{subequations}
which indicates that no corrections in energy are present 
when transforming
$\varepsilon_{\mathrm{SL}}(\omega)$ to $\alpha_{\mathrm{2D}}(\omega)$.
Performing the simulations at the level of G$_{0}$W$_{0}$
we observe blue shifts in energy in $\varepsilon_{\mathrm{SL}}(\omega)$ 
with increasing $L$. Figures \ref{fig:GW-omega-in} and
\ref{fig:GW-omega-out} show that not only the magnitudes of the dielectric
functions change with $L$ but also the peak positions. As a result
the obtained polarizabilities also show $L$-dependent peak 
shift (Figures \ref{fig:GW-omega-in} {\bf b}-{\bf d} and
\ref{fig:GW-omega-out}{\bf b}-{\bf d}). This 
can be explained by the long-range nature of the 
Coulomb interactions into the self-energy 
$\Sigma=iGW$.

@@

In general terms excitonic effects are not taken into account at the level of PBE or 
G\textsubscript{0}W\textsubscript{0}. 
%
%
%
%For bulk systems, the most accurate simulations are based on BSE approach for 
%the optical properties. As excitonic effects including electron-hole interactions are taken 
%into account 
% 
%This is because the calculation of the frequency-dependent
%optical properties of a material involves a summation over the valence
%and conduction states. 
%
%Thus, the accuracy of these states determines
%the calculated optical properties. 
%
%Within Kohn-Sham density functional
%theory (KS-DFT), the many-body effects are given by the
%exchange-correlation energy which is approximated by functionals based
%on the homogenous electron gas. 
%% 
For the former, this generally leads to an 
underestimation of the electronic bandgap and results in the first optical peak
being lower in energy in comparison to more accurate methods. 
To go beyond
PBE, the G\textsubscript{0}W\textsubscript{0} approximation
replaces the exchange-correlation energy by the self-energy 
to include many-body effects through the interacting Green's function,
$G$, and the screened Coulomb potential, $W$. 
%
This generally leads to
an overestimation of the first optical peak as electron-hole coupling
is not taken into account. This can be remedied by solving the
Bethe-Salpeter equation using the eigenvalues obtained from
G\textsubscript{0}W\textsubscript{0}
(G\textsubscript{0}W\textsubscript{0} - BSE) which generally gives
good agreement with experiment.

Due to the volume dependence of $\Sigma$ in equations \ref{self} and
\ref{quasi}, increasing the vacuum spacing leads to a change in the
calculated quasi-particle eigenergies. This, along with the volume
dependence in the calculation of the dielectric function, leads to an
increase in energy of the peak position and a decrease in its
magnitude with increasing vacuum spacing. Such effect is also
discussed in several other studies
\cite{Rozzi_2006,Hueser_2013_2Dvs3D}, when full Coulomb interaction is
used in a supercell. Including excitonic effects on top of a
G$_0$W$_0$ calculation through solving the Bethe--Salpeter equation
correct this energy shift by localizing the exciton within the
slab (Figures \ref{fig:BSE-omega-in} and
\ref{fig:BSE-omega-out}). However, the decrease in the magnitude of
the dielectric function on both components of
$\varepsilon_{\mathrm{SL}}(\omega)$ with increasing vacuum spacing is
still observed.  Using main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def} we can remove the dependence on $L$ as
plotted in Figures \ref{fig:BSE-omega-in}{\bf b}-{\bf d} and
\ref{fig:BSE-omega-out}{\bf b}-{\bf d} with fewer variations on
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$.

@@

Combining the accuray of bandgap estimation, reproducible results of
frequency-dependent dielectric properties and calculation efforts, the
choice of HSE06 hybrid functional used in the main text provides
best trade off between all aspects.

@@

The major issue when using rescale
relations \ref{main-Response:1}$-$\ref{main-eq:emt-2} comes from the determination of $\delta_{\mathrm{2D}}^{*}$. To
eliminate the modeling error caused by the \textit{a priori} selection of this parameter, 
we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
and use least-square fitting to extract both
$\varepsilon$ and $\delta$, as shown in
Figure \ref{fig:rescale-prb}.
%
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.85\linewidth]{img/SI-rescale-PRB.pdf}
  \caption{ Calculated (blue dots) and fitted
    (orange broken lines) $\varepsilon_{\mathrm{SL}}$ as function of
    $L$ for the group 6 TMDCs:
    \textbf{a}. MoS$_{2}$. \textbf{b}. MoSe$_{2}$. \textbf{c}.
    MoTe$_{2}$. \textbf{d}. WS$_{2}$. \textbf{e}. WSe$_{2}$. \textbf{f}.
    WTe$_{2}$. The extracted values of $\varepsilon_{\mathrm{2D}}$ and
    $\delta$ are shown in each subfigure.}
  \label{fig:rescale-prb}
\end{figure}
%
The values of $\delta_{\mathrm{2D}}^{*}$ extracted
from both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ are close when $L> 15$
{\AA}. Notably, the $\delta_{\mathrm{2D}}^{*}$ values are generally 10\%
smaller than the interlayer distance in corresponding bulk materials
$L_{\mathrm{\rm Bulk}}$, as shown in Table \ref{tab:delta-L-DFt}. On the
other hand, the extracted $\delta_{\mathrm{2D}}^{*}$ values are closer to
the covalent thickness $\delta_{\rm cov}$ as
described in the main text, with a difference generally smaller than
5\%. Our results indicate that the conventional estimation of the 2D
layer thickness by its bulk interlayer distance
\cite{Matthes_2016,Laturia_2018}, will always lead to
overestimation. On the contrary, the out-of-plane polarizability
$\alpha_{\mathrm{2D}}^{\perp}$ correctly captures the thickness 
of 2D materials.

@@

One main drawback of the EDM approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable (within a range of 8-13\%) or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{main-eq:emt-2} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta^{*}_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}
%
%
which indicates that the characteristic length
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
than $\delta_{\mathrm{2D}}^{*}$ estimated by the effective medium theory,
if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}^{*}$ and
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
$\delta_{\mathrm{2D}}^{*}$ chosen may lead to divergence of
$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
\ref{fig:eps-alpha-error}. Therefore cautions must be taken when
treating the dielectric response of the 2D material using effective
medium theory. In comparison, the 2D polarizability does not require
the initial guess of the thickness.

@@

To conclude, based on theoretical and technical considerations, there are several
advantages of using the electronic polarizability for describing the dielectric
nature of 2D materials, including:
%
\begin{enumerate}
\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ is unable.

\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length at relative small $L$, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length. This is a big advantage on the computational side since the larger the supercell the larger the computational cost.

\item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.

\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.

\item The value of $\epsilon_{\mathrm{2D}}$ hugely depends on the
  choice of the thickness of 2D material, while such information is
  intrinsically embedded in $\alpha_{\mathrm{2D}}$.
\end{enumerate}
%
%

%%%%%%%%%%%%%%%%

\subsection{Derivation of Eqs.\ref{main-eq:alpha-para-def} and \ref{main-eq:alpha-perp-def}}

To show that Eqs. \ref{main-eq:alpha-para-def} and \ref{main-eq:alpha-perp-def} do not use any arguments based on EMT but rather basic electrostatics, we show the derivation of both equations in the following.

\subsubsection{Parallel to the surface}

For in-plane electric field, the electrostatic boundary conditions gives the continuity of the applied electric field as  
${E}^{\parallel}_{\mathrm{loc}}={E}^{\parallel}$\cite{Markel_2016}, which resulted in 
${P}^{p}=\frac{1}{L} {\mu}^{p}_{\mathrm{2D}}$. Indeed, ${\mu}^{p}_{\mathrm{2D}}$ can be written in terms of the local electric field ${E}_{\mathrm{loc}}^{p}$ and the 2D polarizability $\alpha_{\mathrm{2D}}$ as:

\begin{equation}
{\mu}^{p}_{\mathrm{2D}} = \alpha^{\parallel}_{\mathrm{2D}} {E}^{\parallel}_{\mathrm{loc}} 
\end{equation}
%
This gives for the in-plane polarization:
